Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-13 thesis/experiment.tex
Refer to netAI in it's properly formatted name.

The data captured was in the form of 1MB capture files which were recombined
with mergecap and processed by NetAI to produce ARFF format files for use by
Weka. NetAI identifies flows inside the capture files and produces a number
of statistics to be used as attributes for classification. The statistical
attributes produced by NetAI are shown in table \ref{table:netmate-attributes}.

>>>>

The data captured was in the form of 1MB capture files which were recombined
with mergecap and processed by netAI to produce ARFF format files for use by
Weka. netAI identifies flows inside the capture files and produces a number
of statistics to be used as attributes for classification. The statistical
attributes produced by netAI are shown in table \ref{table:netmate-attributes}.
